Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2024-02-14 news.Rmd
news

@@

>>>>

- Participated at the UNESCO Global AI Ethics Forum (more on this in this [LinkedIn post](https://www.linkedin.com/posts/andreskarjus_aiethics-ai-activity-7159597653553524736-VnZv?utm_source=share&utm_medium=member_desktop) and Twitter/X [threads](https://twitter.com/AndresKarjus)) (February 2024)

- Meanwhile, have done more AI workshops for schools and university departments across Estonia (details&booking requests see [here](datafigure.eu))

@@

- Joined Estonian Business School as a senior research fellow, initially part-time; continuing also at Tallinn University.
